Molecular Gas Dynamics of the strongly-lensed wet-merger RXS J1131-1231 at $z$=0.654

### 2016-07-05 WRITEUP/ms.tex
done intro sec

\begin{abstract}
We report interferometric observations of \bco and \cco emission toward the gravitationally lensed 
quasar RXS J1131-1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
This is the first resolved \bco imaging at intermediate redshift.
RXS J1131-1231 ?. 
evidence for differential lensing.
wet-merger, Dynamical lens modeling
the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
is indicative of, and suggests...
% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
% MBH-sigma relation...
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
Despite the recent progress in theoretical models and observational studies...on understanding the evolution of massive galaxies.
% interplay between / role of Complex baryonic physics such as mergers, gas dissipation, and feedback..
It is not known when and how the main baryonic components of modern galaxies formed/assembled, but the global 
stellar mass density rose substantially between z\ssim1$-$3, reaching $\sim$50\% of its present value by z\ssim1 
(\ie how high-z galaxies evolve into present-day galaxies.)
As such, studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 is important to unravel/understand the cause for the rapid decline in star formation and BH accretion rates (e.g. Madau et al. 1998, Hopkins \& Beacom 2006). 
Studies of galaxy evolution find SFRD and BHAH peak at
$z$\ssim2 and declines rapidly toward $z$$=$0. A leading explanation for such
a trend is the evolution of molecular gas content and SFE in galaxies (CW13).
While we know blah at the local universe and studies of the gas properties at
high-z are also emerging in recent years (see CW13 for a review). It is still
unclear what mechanism is responsible for removing cold gas from galaxies and
shutting down their star formation to build-up present-day red sequence
galaxies, leading to a change of slope at high \mstar (esp. at $z$ $<$ 1.5),  i.e.
suppression of SFR at high \mstar, i.e. strong evolution in sSFR (of massive gal.)
(cite: Papovich, Whitaker+12, Magnelli+14, Schreiber+15, Lee+15).
It has been proposed that the high SFR at high-$z$ is due to the higher gas fraction than local (Erb et al. 2006), 
regardless of their position in the SFR$-$M$^*$ plane, both MS and SB at high z have depletion time that is much 
short than local, suggesting more efficient mode for SF. 
Up to now, very little is known about the molecular gas content at moderate z. The ULIRG sample of Solomon97 contains 37 objects, but only 2 at are z $>$ 0.2. With the advance in mm-instruments, Combes11a investigate the variation of molecular gas and SFE in an expanded sample of 30 ULIRGs with CO observations.

%why AGN host 
In the current paradigm, SMBHs grew in every massive galaxy during a luminous quasar phase, 
where distant QSOs are the progenitors of the passive SMBHs in nearby galaxies.
Locally, the connection between AGNs and their host galaxies is described 
through the well-established tight correlation between BH mass 
and stellar velocity dispersion (CITE), implying growth of the SMBH and their host galaxies is co-eval.
However, it is unclear if this relation holds/or how the co-evolution BLAH at high-$z$.
Recently, theoretical and observational studies of the co-evolution of SMBHs and their host galaxies
have been attempting to extend this relation out to higher-$z$, beyond the peak epoch 
of \SF and AGN activity (CITE).

% difference proxy to the relation
Since it is not trivial to obtain measurement of stellar dispersion (rely on spatially resolved stellar kinematics) at high-$z$, 
efforts in calibrating and understanding how 
the use of dynamical mass or stellar bulge mass \citep[\eg][]{Peng06a} or 
stellar luminosity as a proxy for stellar dispersion.
At high-$z$, more CO measurements have been obtained at high-z, and
one can obtain dynamical mass through CO linewidth and spatial extent.

Based on the \mbh$-$\mdyn relation, there are considerable evidence now that high-z BHs grow faster than their host galaxies.
The dynamical mass inferred from CO velocity structure (line width) and spatial extent is lower than that 
based on local relation. 
Current results imply high-$z$ galaxies ($z$$>$BLAH) do not follow this relation, where their observed $M_\textrm{dyn}$ is lower than that inferred from
this relation or \mbh$/$$M_{*}$ is smaller high-$z$ than today \citep{Borys05a}. 
This implies that a quasar phase is needed in order for high-z galaxies to evolve 
onto the local \mbh$-$$M_{\rm bulge}$ relation / high-$z$ BH grow faster than their host galaxies, 
as predicted in simulations where feedback is needed in order to explain the 
anti-hierarchical growth of galaxies / suppress efficient early star formation
and the lack of more massive galaxies as would be produced without feedback. 
But how investigate this evolution at intermediate redshift is challenging,
because it also suffers the same cosmological dimming issue at high-$z$ studies, time-consuming to obtain
resolved CO observations for intermediate-z.

One way to understand is to investigate the relation as different epochs more closely.
We still lack a clear picture of relationship between AGN and hosts since we do not know much at the intermediate redshifts where both \SF and AGN accretion slow down.
It appears that there may be a decreasing trend from $z$$>$3 to 1$<$3 and compared to the local fit.
But it is clear that there is a desert in between these redshift range.

Host galaxies of AGN are difficult to study because the quasar usually dominates the observed light, and ?.
With gravitational lensing, the stellar emission and quasar emission in RXJ1131 
are magnified and stretched out at different locations to different extents in the image plane, gaining 
the surface brightness contrast to enable measurements of their emission separately.
RXJ1131 thus provide a unique laboratory to study the ?

%--------
In this paper, we explore the well-established local BLAH relations to intermediate redshift
and investigate the postulated decrease gas fraction from BLAH studies at intermediate 
redshift.
We use BLAH to study the ISM properties of the quadruply imaged
quasar RXS J113151.62-123158 (hereafter RXJ1131) at
$z_\textrm{s, QSO}$\eq0.685, lensed by an
elliptical galaxy at $z_\textrm{L}$\eq0.295. The redshifts 
are spectroscopically confirmed by \citet[hereafter S03]{Sluse03a}.
Emission in the host galaxy of RXJ1131 is lensed into an Einstein ring of size 1\farcs83 in radius.
The black hole of mass \mbh\,$<$\,2\E{8}\Msun\footnote{Various values for the black hole 
mass have been reported based on the different methods and normalizations used. \citet{Dai10a} find a 
\mbh\ssim10$^{8}$\,\Msun using the virial estimator with H$\beta$ linewidth,
and \citet{Pooley07a} report $M_{\rm BH}$\,=\,2.5\E{7}\,\Msun using the
AGN bolometric luminosity of $L_{\rm bol, X}$ =1.3\E{45}\, ergs\,s\pmOne, 
assuming $L$$/$$L_\textrm{Edd}$ = 0.25 and $\eta$ = 0.15.}
residing in RXJ1131 has been observed to 
be rotating with a high spin parameter
\citep[$a$\,$\sim$\,0.9;][]{Reis14a}.
\defcitealias{Sluse03a}{S03}

This paper is structured as follows.
In \Sec{obs} and \Sec{HST}, we outline the details of the observations and data reduction process.
In \Sec{results}, we report the measurements of the CO lines and photometry from optical to radio wavelengths.
In \Sec{anal}, we present dynamical lens modeling of the \bco data and the physical properties inferred for  RXJ1131.
In \Sec{diss}, we discuss the results and implications of this study in the context of molecular gas in mergers and ULIRGs {\bf BLAH}.
Finally, we summarize the main results of this study and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = 69.32 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.29, and
$\Omega_{\Lambda}$ = 0.71 \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo

@@

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
% rms scatter over ~ 90 klambda
% max baseline of obs. is 145 m
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
%
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$60$\degr$ over a baseline length of $\sim$135\,m.
%BLAH... more like 50%
We thus conservatively estimate
a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat its line intensity with caution and ensure that our physical interpretation
of this system does not rely on this quantity.

@@

\section{HST astrometry} \label{sec:HST}
We obtained an {\it HST} image taken with
the ACS/Wide Field Camera 
using the F555W filter ($V$-band)
from the
Hubble Legacy Archive\footnote{Based on observations
made with the NASA/ESA Hubble Space Telescope, and obtained from the Hubble
Legacy Archive, which is a collaboration between the Space Telescope Science
Institute (STScI/NASA), the Space Telescope European Coordinating Facility
(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}. 
The details of the observations can be found
in \citet[hereafter C06]{Claeskens06a}.
We adopt the VLA 5\,GHz map as the
reference coordinate frame to align the optical ($V$-band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. This astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have an astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR and phase
instability.
\defcitealias{Claeskens06a}{C06}

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21} %DONE
We detect \bco line emission toward the background source
at $\gtrsim$27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.65370\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry as a result of differential lensing.
A detailed discussion of this effect is presented in
\Sec{differential} and the magnification factors for various kinematic
components are listed in \Tab{model}.
 \label{fig:CO21spec}}
\end{figure}

@@

The deconvolved source size FWHM from two-dimensional Gaussian fitting
is estimated to be 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, we therefore take this as an estimate on the extent of the lensed
emission. On the other hand, if we assume the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and
the lensed knots (see \Fig{CO21mom}).

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/de-lensedSpecCO21_complicated_unbinned_ylog.eps}
\caption{The full resolution \bco spectrum (yellow histogram) and 
the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The 
blue histogram shows the ``intrinsic'' line profile of RXJ1131 
after subtracting a contribution from its companion galaxy and 
correcting for lensing using the magnification factors $\mu_{\rm L}$ as annotated with horizontal bars
above the respective model channels. Flux density is shown on a log scale along the y-axis.
\label{fig:delensed}}
\end{figure}

@@

\subsubsection{Gas Mass and Gas Ratios}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% gas to dust ratio:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Solomon+97: GDR ~ 100
% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
% our galaxy MW ~150 (Draine+07)
% 120 (Li & Draine 2001) to ?160 (Zubko et al. 2004) to ?180 (Draine et al. 2007, and references therein)
% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Using the lensing-corrected dust mass, we find a galactic-scale gas-to-dust ratio of
40\pmm34, which is lower than the statistical average of $f_{\rm gas-dust}$\,=\,206
in the \citetalias{Combes13a} sample but well within their broad 
range of values over the entire sample. Our ratio is also consistent with 
high-$z$ SMGs 
% \citep[78\pmm26;][]{Bothwell13a} 
\citep[hereafter B13]{Bothwell13a} and
local ULIRGs \citep{Wilson08a}, but lower than of the Milky Way by
$\sim 4\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
We note that the dust mass derived for RXJ1131 is poorly constrained.
If we adopt a dust mass from the other SED fit (\ie without constraints at 24\,$\micron$),
the dust mass is reduced by a factor of $\sim$2. \defcitealias{Bothwell13a}{B13}

@@

\subsection{The \bhrelation Relation}

Comparing the spatial extents of the CO with the stellar components traced by {\it HST}\\
The dusty nature of this system?? \\

@@

% explicit discussion of RXJ1131 being IR luminous, and gas-rich
Our analysis of the cold gas kinematics and dynamics of RXJ1131 find 
characteristics resembling a rotating disk. 
The intrinsically symmetric double-horned line profile, the smooth and
symmetric velocity field/gradient seen in both the source plane from our lens model as well
as in the image plane, consistent with the findings from previous optical lens model 
suggesting a kinematically-order rotating disk galaxy.
The high dispersion $\gtrsim$400\,\kms near the dynamical center also
suggest that RXJ1131 is turbulent, albeit lack of spatial resolution. 
Our results confirms the presence of the optically faint companion with CO detection
suggested by previous studies. 
Assuming same CO excitation, we find a gas mass of BLAH in
the companion. Using the gas mass ratio of ($\sim$7:1)between RXJ1131 and the companion, this 
implies the system is a wet minor merger.
We thus conclude that RXJ1131 is a ULIRG hosting a massive gas reservoir in a disturbed/turbulent
disk, undergoing merging with a nearby companion (aka a wet minor merger).

The SFE is similar to that nearby spiral galaxies and high-$z$ disk-like galaxies rather than 
ULIRGs or high-$z$ starbursts galaxies at $z$$\gtrsim$0.6. Implying BLAH
Our result is consistent with the emerging consensus on
the correlation between molecular gas content and redshift,
suggesting it as the explanation for the elevated SFR at high redshift/
the observed trend in the cosmic SFH.
Given our large error bar on the gas mass fraction, we cannot constrain its evolution 
but our result is consistent with a decreasing trend of gas fraction
since $z$\,$\approx$\,1.0 \citep{Combes13a}; but is consistent with 
in both ULIRGs samples in redshift bins of 0.2\,$<$\,$z$\,$<$\,0.4 and 0.6\,$<$\,$z$\,$<$\,1.0 within the uncertainties.

The compact UV emission, which can be a starburst resulting from gas accumulation
owing to a non-axisymmetric perturbation from the companion.
% the stellar component torques away the angular momentum, allowing the gas to fall inward.
Dusty nature of companion?
The IR luminosity also agrees with the results from previous low-$z$ studies: AGNs are
typically found in late stage mergers \citep{Yuan10a,Iwasawa11a,Carpineti12a} and
only major mergers near their final coalescence can provide \LIR$>$\,10$^{12}$\,\Lsun,
\citep[\eg][]{Carpineti15a,Larson16a}. In contrast to the 
galaxies with ULIRG-like IR luminosity high-$z$, are believed to be in some stages of merging.

The highly spinning black hole in RXJ1131 is also consistent with
this hypothesis.
If we favor the gravitational wave recoil mechanism
to explain the optical velocity offset, it would also imply the black
holes (and their host galaxies) have merged or are at their final coalescence.

The optical lines are at a velocity offset of $\sim$780\,\kms from the systematic redshift is consistent 
with possible black hole recoil. 
Given the BLAH, it is plausible that RXJ1131 is in its late stage of merging and 
possibly encountered with its companion previously, consistent with 
compact SB traced by $V$-band image triggered by gas inflow/accumulation toward nuclear regions 
arising from perturbations in the disk from/interactions with the companion.
%Our results indicate a self-consistent picture of ... followed by gravitationally instability and SF in a massive, gas-rich disk and a subsequent build-up of a central bulge through inflow triggered by disk installbilities and/or minor merger.
Theoretical simulations suggest disk in progenitor galaxy may be retained post-merging in gas-rich 
mergers. BLAH. Thus, the merging system studied here will likely evolve into a merged disk galaxy.

>>>>

\begin{abstract}
We present interferometric observations of \bco and \cco emission toward the gravitationally lensed 
quasar RXS J1131-1231 at $z$\,=\,0.654, obtained with the \pdbi and \carma. 
Spatially and spectrally resolved.This is the first resolved \bco imaging at intermediate redshift.
The molecular gas of $M_{\rm gas}$\eq123BLAH\E{10}\,\Msun in the host galaxy 
is extended ($\sim$6\,kpc). An optically faint companion galaxy with gas mass BLAH (gas mass ratio 1:7). 
RXS J1131-1231 ?. 
evidence for differential lensing.
wet-merger, Dynamical lens modeling
the intrinsic dynamics and blah are suggestive of a rotating disk morphology , consistent with previous results based on optical observations.
is indicative of, and suggests...
% Our results is consistent with the picture that gas-rich mergers may evolve into small bulge disk galaxies.
The gas mass fraction of $\sim$19\%, consistent with the trend of decreasing gas fraction at this epoch.
% MBH-sigma relation...
\end{abstract}

@@

%--------------------------------------------------------------------------
%                                Introduction
%--------------------------------------------------------------------------
\section{Introduction}
Studies of galaxy evolution have been focusing on the interplay between baryonic physics
(\eg feedback and gas dissipation) and \SF and active galactic nucleus (AGN) activity across cosmic epochs.
It is not well-understood when and how baryons of present-day galaxies were assembled, 
but it is clear that both the co-moving \SF rate and black hole accretion rate densities
increased substantially since $z$\,$>$\,3 and reached their climax at $z$\ssim2, followed by 
a rapidly decline toward $z$\ssim0 \citep[\eg][]{Hopkins06a, Madau14a}. 
% Studying the cold gas at the redshift range 0.2 $<$\,$z$\,$<$\,1 of paramount importance to ravel the cause for this decline.
A leading explanation for this decline is related to the evolution of molecular gas content and 
\SF efficiency \citep[]{Erb06a, CW13, Walter14a},
but confirmation from direct molecular gas measurements at intermediate redshift 
$($0.2\,$<$\,$z$\,$<$\,1$)$ is still limited both in number and in the variety of galaxy populations probed --- 
only unresolved CO observations have been carried out for $\sim$\,70 ULIRGs up to date \citep{Combes11a, Combes13a}.

% - nearby: fixed proportion in M_BH to the M* in the bulge: ~0.1-0.2%
In the current paradigm, it is posited that every nearby, massive galaxy host a supermassive black hole (SMBH), which
grows by accretion of the cold molecular gas from its host galaxy.
Meanwhile, empirical scaling relations such as the Magorrian relation \citep{Magorrian98a}
--- a tight correlation between black hole mass and stellar bulge mass ---
have been established locally, implying a self-regulating co-eval growth between local SMBHs and their host galaxies.
Attempts to extend this relation out to higher redshifts, beyond the peak epoch 
of \SF and AGN activity, have been made in recent years.
It has been reported that the $M_{\rm BH}$$/$\mstar ratio of high-$z$ galaxies falls below 
the local relation \citep[\eg][]{Walter04a, Borys05a, Riechers08a, Riechers08b}, implying 
high-$z$ AGNs grow faster than their host galaxies.
Yet, this relation is currently unconstrained at intermediate redshifts owing to the difficulties in measuring 
the stellar emission in the host galaxy under the presence of a quasar, or alternatively
the lack of spatially resolved CO observations to provide dynamical constraints on the stellar mass. 
With gravitational lensing, emission of the background quasar and its host galaxy 
is magnified and stretched out to different extents, and is projected to different locations in the image plane.
This in effect increases the surface brightness contrast between their emission and allows for
their measurements in a relatively uncontaminated/independent manner.

In this paper, we study the molecular gas and dust properties of the quadruply imaged
quasar RXS J113151.62$-$123158 (hereafter RXJ1131) at
$z_\textrm{s, QSO}$\eq0.685 as lensed by an
elliptical galaxy at $z_\textrm{L}$\eq0.295. These redshifts 
are spectroscopically confirmed by \citet[hereafter S03]{Sluse03a}.
In the {\it HST} images presented by \citet[hereafter C06]{Claeskens06a}, emission 
in the host galaxy of RXJ1131 is lensed into an Einstein ring of size 1\farcs83 in radius and
the quasar emission is lensed into four point-like images.
The black hole of mass \mbh\,$<$\,2\E{8}\Msun\footnote{Various values for the black hole 
mass have been reported based on the different methods and normalizations used. \citet{Dai10a} find a 
\mbh\ssim10$^{8}$\,\Msun using the virial estimator with H$\beta$ linewidth,
and \citet{Pooley07a} report $M_{\rm BH}$\,=\,2.5\E{7}\,\Msun using the
AGN bolometric luminosity of $L_{\rm bol, X}$ =1.3\E{45}\, ergs\,s\pmOne, 
assuming $L$$/$$L_\textrm{Edd}$ = 0.25 and $\eta$ = 0.15.}
residing in RXJ1131 has been observed to 
be rotating with a high spin parameter
\citep[$a$\,$\sim$\,0.9;][]{Reis14a}.

This paper is structured as follows.
In \Sec{obs}, we outline the details of the observations and our data reduction process.
In \Sec{HST}, we describe our astrometric corrections applied to align an {\it HST} image with our radio maps.
In \Sec{results}, we report the measurements of the CO lines and photometry from optical to radio wavelengths.
In \Sec{anal}, we present dynamical lens modeling of the \bco data, SED modeling of the thermal dust continuum, 
and the resulting physical properties inferred for RXJ1131.
In \Sec{diss}, we discuss the merger stage of RXJ1131 and implications of 
this study in the context of the evolution of molecular gas content
and the $M_{\rm BH}$$-$\mdyn relation at intermediate redshift.
Finally, we summarize the main results and present our conclusions in \Sec{sum}.
We use a concordance $\Lambda$CDM cosmology throughout this paper, with
parameters from the WMAP9 results:
$H_0$ = 69.32 \kms Mpc\pmOne, $\Omega_{\rm M}$ = 0.29, and
$\Omega_{\Lambda}$ = 0.71 \citep{Hinshaw13a}.
% same as LR16a: i.e. use last column (WMAP+eCMB+BAO+H0) of Tab 4 in Hinshaw+13 because that's what astropy use for WMAP9 as cosmo
\defcitealias{Sluse03a}{S03}
\defcitealias{Claeskens06a}{C06}

@@

% poor phase note
% /Users/admin/Research/RXJ1131/CARMA/imagingD23/checkQuality.csh
% rms scatter over ~ 90 klambda
% max baseline of obs. is 145 m
%
% calflux source=1127-189 in=$MIRCAT/FluxSource.cat device=/xs
% Flux of: 1127-189  14FEB04.50 at 227.0 GHz:  0.65 Jy; rms: 0.10 Jy
% Extrapolate to 215.673 GHz with spectral index = -0.986 --> 0.684 Jy
% MIRIAD from bootstrap: Median Flux @ 215.673 GHz:     0.710
%
Given that the phase calibrator used for the first track was faint and was
observed under poor weather conditions and that the phase calibrator used for
the second track was far from our target source, the phase calibration is
subpar, with an rms scatter $\sim$60$\degr$ over a baseline length of $\sim$135\,m.
%BLAH... more like 50%
We thus conservatively estimate
a calibration accuracy of $\sim$45\% based on the flux scale uncertainties,
the gain variations over time, and the phase scatter on the calibrated data. We
therefore treat its line intensity with caution and ensure that our physical interpretation
of this system and the conclusion of this do not rely on this quantity.

@@

\section{HST astrometry} \label{sec:HST}
We obtained an {\it HST} image taken with
the ACS/Wide Field Camera 
using the F555W filter ($V$-band)
from the
Hubble Legacy Archive\footnote{Based on observations
made with the NASA/ESA Hubble Space Telescope, and obtained from the Hubble
Legacy Archive, which is a collaboration between the Space Telescope Science
Institute (STScI/NASA), the Space Telescope European Coordinating Facility
(ST-ECF/ESA) and the Canadian Astronomy Data Centre (CADC/NRC/CSA).}. 
The details of the observations can be found
in \citetalias{Claeskens06a}.
We adopt the VLA 5\,GHz map as the
reference coordinate frame to align the optical ($V$-band) image.
We shift the latter to the east by 0\farcs5963 in R.A. and $+$0\farcs8372 in
Dec., which is consistent with the typical astrometric precision (1$^{\prime\prime}-$2$^{\prime\prime}$) of
images from the Hubble Legacy Archive\footnote{http://hla.stsci.edu/hla\_faq.
html}. This astrometric correction is critical to avoid artificial spatial
offsets between different emitting regions and to carry out our lens modeling,
in which the absolute position of the foreground lensing galaxy is guided by its
coordinates in the optical image, where its emission is clearly detected.
The VLA image is calibrated using a well-monitored phase
calibrator, with absolute positional accuracy of $\sim$2 mas.
For this reason, the absolute alignment between the VLA image and other
interferometric images reported in this paper are expected to have an astrometric
precision better than 0\farcs1, modulo uncertainties related to the SNR and phase
instability.

%--------------------------------------------------------------------------
%                                Results
%--------------------------------------------------------------------------
\section{Results} \label{sec:results}
\subsection{\bco Emission} \label{sec:CO21} %DONE
We detect \bco line emission toward the background source
at $\gtrsim$\,27$\sigma$ significance, confirming the redshift at $z_{\rm CO}$ =
0.65370\,$\pm$\,0.0005. The emission is spatially and dynamically resolved
with a highly asymmetric double-horned line profile
as shown in \Fig{CO21spec}. Fitting a double Gaussian results in peak
flux densities of 75.3\pmm2.6 and 24.0\pmm2.0 mJy, and a FWHM of
179\pmm9 \kms and 255\pmm28 \kms for the two components, respectively. The peaks are separated by
$\Delta v_{\rm sep}$ = 400\pmm12\,\kms. The total integrated line flux is 24.1\,$\pm$\,2.3 Jy \kms. % see 15May16/

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/SpecCO21_twinx.eps}
\caption{ Spectrum of \bco emission toward RXJ1131. The velocity scale
is with respect to $z$\,=\,0.6537, which is approximately the line center
considering the asymmetry as a result of differential lensing.
A detailed discussion of this effect is presented in
\Sec{differential}.
 \label{fig:CO21spec}}
\end{figure}

@@

The deconvolved source size FWHM from fitting a two-dimensional Gaussian
is 5\farcs1\pmm0\farcs72 $\times$ 3\farcs72\pmm0\farcs66,
and thus, the emission is resolved over $\sim$2.2 beams.
While the lensed emission is not strictly distributed as a two-dimensional
Gaussian;
the fit recovers the line intensity enclosed by the emitting
region, we therefore take this as an estimate on the extent of the lensed
emission. On the other hand, if we assume that the spatial distribution of
the lensed molecular gas emission is similar to that in the optical to \nir
wavelengths, the lensed emission would be more accurately described by an
annulus, enclosing the partially complete ``Einstein ring'' and
the lensed knots (see \Fig{CO21mom}).

@@

\begin{figure}[!htbp]
\centering
\includegraphics[width=0.45\textwidth]{../Figures/de-lensedSpecCO21_complicated_unbinned_ylog.eps}
\caption{The full resolution \bco spectrum (yellow histogram) and 
the binned spectrum (dashed line) with the seven $\Delta v$\,$\sim$\,105\,\kms channels used for lens modeling. The 
blue histogram shows the ``intrinsic'' line profile of RXJ1131 
after subtracting a contribution from its companion galaxy and 
correcting for lensing using the magnification factors $\mu_{\rm L}$ as annotated by the horizontal bars shown
above the respective model channels. Flux density on the y-axis is shown on a log scale.
\label{fig:delensed}}
\end{figure}

@@

\subsubsection{Gas Mass and Gas Ratios}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% gas to dust ratio:
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Solomon+97: GDR ~ 100
% single disk: 90 (converted conversion factor to 0.8) (Sanders91a)
% our galaxy MW ~150 (Draine+07)
% 120 (Li & Draine 2001) to ?160 (Zubko et al. 2004) to ?180 (Draine et al. 2007, and references therein)
% Wilson+08: U/LIRGs: abstract: 120+/-28 (rms deviation 109) in the most central kpc; paper content: 215+/-53 (rms 207); but 50-70 for ULIRGs only
%
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Using the lensing-corrected dust mass, we find a galactic-scale gas-to-dust ratio of
40\pmm34, which is lower than the statistical average of $f_{\rm gas-dust}$\,=\,206
in the \citetalias{Combes13a} sample but well within their broad 
range of values over the entire sample. Our ratio is also consistent with 
high-$z$ SMGs 
% \citep[78\pmm26;][]{Bothwell13a} 
\citep[]{Bothwell13a} and
local ULIRGs \citep{Wilson08a}, but lower than of the Milky Way by
$\sim 4\sigma$ \citep[ignoring systematic uncertainties;][]{Li01a,Zubko04a,Draine07a}.
We note that the dust mass derived for RXJ1131 is poorly constrained.
If we adopt a dust mass from the other SED fit (\ie without constraints at 24\,$\micron$),
the dust mass is reduced by a factor of $\sim$2. \defcitealias{Bothwell13a}{B13}

@@

\subsection{The \bhrelation Relation}
Comparing the spatial extents of the CO with the stellar components traced by {\it HST}\\
The dusty nature of this system?? \\

Efforts have been invested into calibrating and understanding how 
the use of or dynamical mass \citep[\eg]{Shields06a} 
as a proxy for stellar dispersion or bulge mass.

@@

% explicit discussion of RXJ1131 being IR luminous, and gas-rich
The intrinsically symmetric double-horned line profile, the smooth and
symmetric velocity field/gradient seen in both the source plane from our lens model as well
as in the image plane are characteristics resembling a rotating disk, 
consistent with the findings from previous optical lens model.
The high dispersion $\gtrsim$400\,\kms near the dynamical center suggest that 
RXJ1131 is turbulent, albeit lack of spatial resolution. 
Our lens modeling analysis also confirms the presence of the optically faint companion 
suggested by previous studies, with CO emission.
Assuming the same CO excitation as RXJ1131 for the companion, we find a gas mass of BLAH,
which implies a gas mass ratio of ($\sim$7:1) between RXJ1131 and the companion. 
We thus classify the system is a wet minor merger.
We conclude that RXJ1131 is a ULIRG hosting a massive gas reservoir in a disturbed/turbulent
disk, undergoing merging with a nearby companion (aka a wet minor merger).

While many characteristics of RXJ1131 resembles local ULIRGs and high-z SBs (such as 
linewidth, CO sizes, SFR, gas mass), its SFE is similar to that nearby 
spiral galaxies and high-$z$ disk-like galaxies rather than 
ULIRGs or high-$z$ starbursts galaxies at $z$$\gtrsim$0.6. 
Our result is consistent with the emerging consensus on
the correlation between molecular gas content and redshift,
suggesting it as the explanation for the elevated SFR at high redshift/
the observed trend in the cosmic SFH.
Given our large error bar on the gas mass fraction, we cannot constrain its evolution 
but our result is consistent with a decreasing trend of gas fraction
since $z$\,$\approx$\,1.0 \citep{Combes13a}; but is consistent with 
in both ULIRGs samples in redshift bins of 0.2\,$<$\,$z$\,$<$\,0.4 and 0.6\,$<$\,$z$\,$<$\,1.0 within the uncertainties.

The compact UV emission, which can be a starburst resulting from gas accumulation
owing to a non-axisymmetric perturbation from the companion.
% the stellar component torques away the angular momentum, allowing the gas to fall inward.
Dusty nature of companion?
The IR luminosity also agrees with the results from previous low-$z$ studies: AGNs are
typically found in late stage mergers \citep{Yuan10a,Iwasawa11a,Carpineti12a} and
only major mergers near their final coalescence can provide \LIR$>$\,10$^{12}$\,\Lsun,
\citep[\eg][]{Carpineti15a,Larson16a}. In contrast to the 
galaxies with ULIRG-like IR luminosity at high redshifts, which can be in early stages of merging.

We find that the optical lines are offset from the systemic redshift by $\sim$780\,\kms, (caution use of optical lines 
as systemic redshift)
may imply a recoiling black hole in RXJ1131, which would imply the black
holes (and their host galaxies) have merged or are at their final coalescence.
The highly spinning black hole in RXJ1131 is also consistent with
this hypothesis.
Given the presence of a companions, it is plausible that RXJ1131 is in its late stage of merging and 
possibly encountered with its companion previously, consistent with 
compact SB traced by $V$-band image triggered by gas inflow/accumulation toward nuclear regions 
arising from perturbations in the disk from/interactions with the companion.
%Our results indicate a self-consistent picture of ... followed by gravitationally instability and SF in a massive, gas-rich disk and a subsequent build-up of a central bulge through inflow triggered by disk installbilities and/or minor merger.
Theoretical simulations suggest disk in progenitor galaxy may be retained post-merging in gas-rich 
mergers. BLAH. Thus, the merging system studied here will likely evolve into a merged disk galaxy.
